CF Registry Analysis - ROC

### 2025-11-18 Christine Chan/CF Registry/cf_registry_ROC_analysis.qmd
cleaned up A1c registry report

```{r setup}
#| include: false
library(dplyr)
library(tidyr)
library(ggplot2)
library(gtsummary)
library(gt)
library(pROC)
library(ggrepel)
home_dir <- switch(Sys.info()["sysname"],
    "Darwin" = "/Users/tim/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry",
    "Windows" = "C:/Users/tim/OneDrive - The University of Colorado Denver/Vigers/CF/Christine Chan/CF Registry",
    "Linux" = "/home/tim/OneDrive/Vigers/CF/Christine Chan/CF Registry"
)
github_dir <- switch(Sys.info()["sysname"],
    "Darwin" = "/Users/timvigers/GitHub",
    "Windows" = "C:/Users/Tim/GitHub",
    "Linux" = "/home/tim/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
set.seed(1017)
```

@@

annual <- annual %>% rename(reviewyear = ReviewYear)
annual <- left_join(annual, demo %>% select(eDWID, Gender), by = join_by(eDWID))
# Get BMI group_by
annual$bmi_cat <- apply(annual, 1, function(r) {

@@

    bmi <- as.numeric(r["A_bmivalue"])
    bmi_perc <- as.numeric(r["A_bmipercentile"])

@@

annual$bmi_cat <- relevel(annual$bmi_cat, ref = "Target/Goal")
    demo %>% select(eDWID, Race, Hispanicrace, Gender, F508, MutClass),
    annual %>%
            bmi_cat,
roc_df <- encounter %>%
    arrange(eDWID, reviewyear, encounternum) %>%
        bmivalue,
        bmipercentile,
        bmi_cat,
        twohour_bloodglucose
    ) %>%
    ) %>%
    group_by(eDWID) %>%
    filter(row_number() == n()) %>%
    ungroup() %>%
# Metrics to report
metrics <- c(
    "thresh",
    "specificity",
    "sensitivity",
    "accuracy",
    "tn",
    "tp",
    "fn",
    "fp",
    "npv",
    "ppv"

@@

```{r}
# Plotting function
roc_plot <- function(roc_obj) {
    c <- coords(roc_obj, "best")
    plot_df <- coords(roc_obj)
    point_df <- plot_df[plot_df$threshold == as.numeric(c[1]), ]
    c <- round(as.numeric(c), 2)
    point_label <- paste0(
        "Threshold: ",
        c[1],
        "\n",
        "Specificity: ",
        c[2],
        "\n",
        "Sensitivity: ",
        c[3]
    )
    p <- ggplot(plot_df, aes(x = specificity, y = sensitivity)) +
        scale_x_reverse() +
        geom_line() +
        geom_point(data = point_df) +
        geom_label_repel(
            data = point_df,
            aes(label = point_label),
            nudge_x = 0.25,
            segment.color = "grey50",
            size = 5
        ) +
        xlab("Specificity") +
        ylab("Sensitivity") +
        theme_bw(base_size = 20)
    return(p)
}
```

@@

```{r}
roc_df %>%
    select(-eDWID) %>%
    tbl_summary(
        by = `OGTT 2-hour`,
        missing_text = "Missing",
        type = list(
            reviewyear ~ "categorical",
            all_continuous() ~ "continuous2"
        ),
        statistic = list(
            all_continuous() ~
                c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}")
        ),
        label = list(
            hgba1c = "HbA1c",
            Hispanicrace = "Hispanic",
            MutClass = "Mutation Class",
            reviewyear = "Year",
            Age_YrEnd = "Age at Year End"
        )
    ) %>%
    add_overall() %>%
    add_p(
        test = list(reviewyear = "fisher.test"),
        test.args = all_tests("fisher.test") ~ list(simulate.p.value = T)
    ) %>%
    separate_p_footnotes() %>%
    as_gt()
```

@@

```{r}
roc_df %>%
    select(
        reviewyear,
        hgba1c,
        Age_YrEnd,
        `Age Group`,
        `OGTT 2-hour`,
        Race,
        Hispanicrace,
        Gender,
        F508,
        MutClass
    ) %>%
    tbl_summary(
        by = `Age Group`,
        missing_text = "Missing",
        type = list(reviewyear ~ "categorical"),
        label = list(
            hgba1c = "HbA1c",
            Hispanicrace = "Hispanic",
            MutClass = "Mutation Class",
            reviewyear = "Year",
            Age_YrEnd = "Age at Year End"
        )
    ) %>%
    add_overall() %>%
    add_p(
        test = list(reviewyear = "fisher.test"),
        test.args = all_tests("fisher.test") ~ list(simulate.p.value = T)
    ) %>%
    separate_p_footnotes() %>%
    as_gt()
```

@@

## NGT vs. AGT and AGT vs. CFRD

@@

1. NGT vs. AGT

2. AGT vs. CFRD

```{r}
ngt_agt <- roc_df %>% filter(`OGTT 2-hour` != ">=200")
ngt_agt$ogtt <- droplevels(ngt_agt$`OGTT 2-hour`)
agt_cfrd <- roc_df %>% filter(`OGTT 2-hour` != "<140")
agt_cfrd$ogtt <- droplevels(agt_cfrd$`OGTT 2-hour`)
```

@@

#### NGT vs. AGT

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

#### AGT vs. CFRD

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
peds_ngt_agt <- ngt_agt %>% filter(Age_YrEnd < 18)
peds_agt_cfrd <- agt_cfrd %>% filter(Age_YrEnd < 18)
```

##### NGT vs. AGT

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = peds_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

##### AGT vs. CFRD

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = peds_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
adult_ngt_agt <- ngt_agt %>% filter(Age_YrEnd >= 18)
adult_agt_cfrd <- agt_cfrd %>% filter(Age_YrEnd >= 18)
```

##### NGT vs. AGT

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = adult_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

##### AGT vs. CFRD

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = adult_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
white_ngt_agt <- ngt_agt %>% filter(Race == "White")
white_agt_cfrd <- agt_cfrd %>% filter(Race == "White")
```

##### NGT vs. AGT

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = white_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

##### AGT vs. CFRD

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = white_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
black_ngt_agt <- ngt_agt %>% filter(Race == "Black or African American")
black_agt_cfrd <- agt_cfrd %>% filter(Race == "Black or African American")
```

##### NGT vs. AGT

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = black_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

##### AGT vs. CFRD

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = black_agt_cfrd)
roc_plot(r)
gt(data.frame(coords(r, "best"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
more_ngt_agt <- ngt_agt %>% filter(Race == "More than one race")
more_agt_cfrd <- agt_cfrd %>% filter(Race == "More than one race")
```

##### NGT vs. AGT

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = more_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

##### AGT vs. CFRD

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = more_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
other_ngt_agt <- ngt_agt %>% filter(Race == "Other race")
other_agt_cfrd <- agt_cfrd %>% filter(Race == "Other race")
```

##### NGT vs. AGT

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = other_ngt_agt)
roc_plot(r)
gt(data.frame(coords(r, "best"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

##### AGT vs. CFRD

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = other_agt_cfrd)
roc_plot(r)
gt(data.frame(coords(r, "best"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
hispanic_ngt_agt <- ngt_agt %>% filter(Hispanicrace == "Yes")
hispanic_agt_cfrd <- agt_cfrd %>% filter(Hispanicrace == "No")
```

##### NGT vs. AGT

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = hispanic_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

##### AGT vs. CFRD

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = hispanic_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
non_hispanic_ngt_agt <-
    ngt_agt %>% filter(Race == "Black or African American")
non_hispanic_agt_cfrd <-
    agt_cfrd %>% filter(Race == "Black or African American")
```

##### NGT vs. AGT

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = non_hispanic_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

##### AGT vs. CFRD

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = roc_df)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

>>>>

```{r setup}
#| include: false
library(dplyr)
library(tidyr)
library(ggplot2)
library(gtsummary)
library(gt)
library(pROC)
library(ggrepel)
library(childsds)
library(labelled)
home_dir <- switch(
  Sys.info()["sysname"],
  "Darwin" = "/Users/tim/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry",
  "Windows" = "C:/Users/tim/OneDrive - The University of Colorado Denver/Vigers/CF/Christine Chan/CF Registry",
  "Linux" = "/home/tim/OneDrive/Vigers/CF/Christine Chan/CF Registry"
)
github_dir <- switch(
  Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/GitHub",
  "Windows" = "C:/Users/Tim/GitHub",
  "Linux" = "/home/tim/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
set.seed(1017)
```

@@

annual <- annual |> rename(reviewyear = ReviewYear)
annual <- left_join(annual, demo |> select(eDWID, Gender), by = join_by(eDWID))
  demo |> select(eDWID, Race, Hispanicrace, Gender, F508, MutClass),
  annual |>
# Format CFTR modulator variables
encounter$Vx770[is.na(encounter$Vx770)] <- 0
encounter$Vx770 <- factor(
  encounter$Vx770,
  levels = 0:1,
  labels = c("No", "Yes")
encounter$Vx809comb[is.na(encounter$Vx809comb)] <- 0
encounter$Vx809comb <- factor(
  encounter$Vx809comb,
  levels = 0:1,
  labels = c("No", "Yes")
roc_df <- encounter |>
  arrange(eDWID, reviewyear, encounternum) |>
    Vx809comb
  ) |>
  ) |>
  drop_na(
    hgba1c
  ) |>
  group_by(eDWID) |>
  filter(row_number() == n()) |>
  ungroup() |>
# Calculate BMI percentiles
roc_df$bmi = roc_df$weight / ((roc_df$height / 100)^2)
roc_df$bmi_perc = sds(
  value = roc_df$bmi,
  age = roc_df$Age_YrEnd,
  sex = roc_df$Gender,
  item = "bmi",
  type = "perc",
  male = "M",
  female = "F",
  ref = cdc.ref
) *
  100
# Raw values for adults
roc_df$bmi_adult = roc_df$bmi
roc_df$bmi_adult[roc_df$Age_YrEnd > 20] = NA
# Get BMI group
roc_df$bmi_cat <- apply(roc_df, 1, function(r) {

@@

  bmi <- as.numeric(r["bmi"])
  bmi_perc <- as.numeric(r["bmi_perc"])

@@

roc_df$bmi_cat <- relevel(roc_df$bmi_cat, ref = "Target/Goal")
# Labels
var_label(roc_df$bmi) = "BMI (all participants)"
var_label(roc_df$bmi_perc) = "BMI percentile (age <= 20)"
var_label(roc_df$bmi_adult) = "BMI value (age > 20)"
var_label(roc_df$bmi_cat) = "BMI category"

@@

```{r}
# Plotting function
roc_plot <- function(roc_obj) {
  a <- ci.auc(roc_obj)
  a <- round(as.numeric(a[1:3]), 2)
  c <- coords(roc_obj, "best")
  plot_df <- coords(roc_obj)
  point_df <- plot_df[plot_df$threshold == as.numeric(c[1]), ]
  c <- round(as.numeric(c), 2)
  point_label <- paste0(
    "Threshold: ",
    c[1],
    "\n",
    "Specificity: ",
    c[2],
    "\n",
    "Sensitivity: ",
    c[3],
    "\n",
    "AUC: ",
    a[2],
    " (95%CI: ",
    a[1],
    ", ",
    a[3],
    ")"
  )
  p <- ggplot(plot_df, aes(x = 1 - specificity, y = sensitivity)) +
    geom_line() +
    geom_point(data = point_df) +
    geom_label_repel(
      data = point_df,
      aes(label = point_label),
      nudge_x = 0.25,
      segment.color = "grey50",
      size = 5
    ) +
    xlab("1-Specificity") +
    ylab("Sensitivity") +
    theme_bw(base_size = 20)
  return(p)
}
```

@@

```{r}
roc_df |>
  select(-eDWID) |>
  tbl_summary(
    by = `OGTT 2-hour`,
    missing_text = "Missing",
    type = list(
      reviewyear ~ "categorical",
      all_continuous() ~ "continuous2"
    ),
    statistic = list(
      all_continuous() ~
        c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}")
    ),
    label = list(
      hgba1c = "HbA1c",
      Hispanicrace = "Hispanic",
      MutClass = "Mutation Class",
      reviewyear = "Year",
      Age_YrEnd = "Age at Year End"
    )
  ) |>
  add_overall() |>
  add_p(
    test = list(reviewyear = "fisher.test"),
    test.args = all_tests("fisher.test") ~ list(simulate.p.value = T)
  ) |>
  separate_p_footnotes() |>
  as_gt()
```

### Pairwise comparisons

#### <140 vs. [140,200)

```{r}
roc_df |>
  select(`OGTT 2-hour`, Gender, MutClass, hgba1c) |>
  filter(`OGTT 2-hour` != ">=200") |>
  mutate(`OGTT 2-hour` = droplevels(`OGTT 2-hour`)) |>
  tbl_summary(
    by = `OGTT 2-hour`,
    missing_text = "Missing",
    type = list(all_continuous() ~ "continuous2"),
    statistic = list(
      all_continuous() ~
        c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}")
    ),
    label = list(
      hgba1c = "HbA1c",
      Hispanicrace = "Hispanic",
      MutClass = "Mutation Class",
      reviewyear = "Year",
      Age_YrEnd = "Age at Year End"
    )
  ) |>
  add_overall() |>
  add_p(
    test = list(reviewyear = "fisher.test"),
    test.args = all_tests("fisher.test") ~ list(simulate.p.value = T)
  ) |>
  separate_p_footnotes() |>
  as_gt()
```

#### [140,200) vs. >=200

```{r}
roc_df |>
  select(`OGTT 2-hour`, Gender, MutClass, hgba1c) |>
  filter(`OGTT 2-hour` != "<140") |>
  mutate(`OGTT 2-hour` = droplevels(`OGTT 2-hour`)) |>
  tbl_summary(
    by = `OGTT 2-hour`,
    missing_text = "Missing",
    type = list(all_continuous() ~ "continuous2"),
    statistic = list(
      all_continuous() ~
        c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}")
    ),
    label = list(
      hgba1c = "HbA1c",
      Hispanicrace = "Hispanic",
      MutClass = "Mutation Class",
      reviewyear = "Year",
      Age_YrEnd = "Age at Year End"
    )
  ) |>
  add_overall() |>
  add_p(
    test = list(reviewyear = "fisher.test"),
    test.args = all_tests("fisher.test") ~ list(simulate.p.value = T)
  ) |>
  separate_p_footnotes() |>
  as_gt()
```

#### <140 vs. >=200

```{r}
roc_df |>
  select(`OGTT 2-hour`, Gender, MutClass, hgba1c) |>
  filter(`OGTT 2-hour` != "[140,200)") |>
  mutate(`OGTT 2-hour` = droplevels(`OGTT 2-hour`)) |>
  tbl_summary(
    by = `OGTT 2-hour`,
    missing_text = "Missing",
    type = list(all_continuous() ~ "continuous2"),
    statistic = list(
      all_continuous() ~
        c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}")
    ),
    label = list(
      hgba1c = "HbA1c",
      Hispanicrace = "Hispanic",
      MutClass = "Mutation Class",
      reviewyear = "Year",
      Age_YrEnd = "Age at Year End"
    )
  ) |>
  add_overall() |>
  add_p(
    test = list(reviewyear = "fisher.test"),
    test.args = all_tests("fisher.test") ~ list(simulate.p.value = T)
  ) |>
  separate_p_footnotes() |>
  as_gt()
```

@@

```{r}
roc_df |>
  select(
    reviewyear,
    hgba1c,
    Age_YrEnd,
    `Age Group`,
    `OGTT 2-hour`,
    Race,
    Hispanicrace,
    Gender,
    F508,
    MutClass
  ) |>
  tbl_summary(
    by = `Age Group`,
    missing_text = "Missing",
    type = list(reviewyear ~ "categorical"),
    label = list(
      hgba1c = "HbA1c",
      Hispanicrace = "Hispanic",
      MutClass = "Mutation Class",
      reviewyear = "Year",
      Age_YrEnd = "Age at Year End"
    )
  ) |>
  add_overall() |>
  add_p(
    test = list(reviewyear = "fisher.test"),
    test.args = all_tests("fisher.test") ~ list(simulate.p.value = T)
  ) |>
  separate_p_footnotes() |>
  as_gt()
```

@@

## NGT vs. (AGT + CFRD) and (NGT + AGT) vs. CFRD

@@

1. NGT vs. (AGT + CFRD)

2. (NGT + AGT) vs. CFRD

```{r}
ngt_agt <- roc_df |>
  mutate(
    ogtt = factor(
      `OGTT 2-hour`,
      levels = c("<140", "[140,200)", ">=200"),
      labels = c("NGT", "AGT + CFRD", "AGT + CFRD")
    )
  )
agt_cfrd <- roc_df |>
  mutate(
    ogtt = factor(
      `OGTT 2-hour`,
      levels = c("<140", "[140,200)", ">=200"),
      labels = c("NGT + AGT", "NGT + AGT", "CFRD")
    )
  )
```

@@

#### NGT vs. (AGT + CFRD)

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
gt(data.frame(coords(
  r,
  "all",
  ret = c(
    "threshold",
    "sensitivity",
    "specificity",
    "tp",
    "tn",
    "fp",
    "fn",
    "npv",
    "ppv",
    "tnr",
    "fnr"
  )
))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
```

#### (NGT + AGT) vs. CFRD

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
gt(data.frame(coords(
  r,
  "all",
  ret = c(
    "threshold",
    "sensitivity",
    "specificity",
    "tp",
    "tn",
    "fp",
    "fn",
    "npv",
    "ppv",
    "tnr",
    "fnr"
  )
))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
```

@@

```{r}
peds_ngt_agt <- ngt_agt |> filter(Age_YrEnd < 18)
peds_agt_cfrd <- agt_cfrd |> filter(Age_YrEnd < 18)
```

##### NGT vs. (AGT + CFRD)

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = peds_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
gt(data.frame(coords(
  r,
  "all",
  ret = c(
    "threshold",
    "sensitivity",
    "specificity",
    "tp",
    "tn",
    "fp",
    "fn",
    "npv",
    "ppv",
    "tnr",
    "fnr"
  )
))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
```

##### (NGT + AGT) vs. CFRD

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = peds_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
gt(data.frame(coords(
  r,
  "all",
  ret = c(
    "threshold",
    "sensitivity",
    "specificity",
    "tp",
    "tn",
    "fp",
    "fn",
    "npv",
    "ppv",
    "tnr",
    "fnr"
  )
))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
```

@@

```{r}
adult_ngt_agt <- ngt_agt |> filter(Age_YrEnd >= 18)
adult_agt_cfrd <- agt_cfrd |> filter(Age_YrEnd >= 18)
```

##### NGT vs. (AGT + CFRD)

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = adult_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
gt(data.frame(coords(
  r,
  "all",
  ret = c(
    "threshold",
    "sensitivity",
    "specificity",
    "tp",
    "tn",
    "fp",
    "fn",
    "npv",
    "ppv",
    "tnr",
    "fnr"
  )
))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
```

##### (NGT + AGT) vs. CFRD

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = adult_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
gt(data.frame(coords(
  r,
  "all",
  ret = c(
    "threshold",
    "sensitivity",
    "specificity",
    "tp",
    "tn",
    "fp",
    "fn",
    "npv",
    "ppv",
    "tnr",
    "fnr"
  )
))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
```

@@

```{r}
white_ngt_agt <- ngt_agt |> filter(Race == "White")
white_agt_cfrd <- agt_cfrd |> filter(Race == "White")
```

##### NGT vs. (AGT + CFRD)

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = white_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
gt(data.frame(coords(
  r,
  "all",
  ret = c(
    "threshold",
    "sensitivity",
    "specificity",
    "tp",
    "tn",
    "fp",
    "fn",
    "npv",
    "ppv",
    "tnr",
    "fnr"
  )
))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
```

##### (NGT + AGT) vs. CFRD

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = white_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
gt(data.frame(coords(
  r,
  "all",
  ret = c(
    "threshold",
    "sensitivity",
    "specificity",
    "tp",
    "tn",
    "fp",
    "fn",
    "npv",
    "ppv",
    "tnr",
    "fnr"
  )
))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
```

@@

```{r}
black_ngt_agt <- ngt_agt |> filter(Race == "Black or African American")
black_agt_cfrd <- agt_cfrd |> filter(Race == "Black or African American")
```

##### NGT vs. (AGT + CFRD)

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = black_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
gt(data.frame(coords(
  r,
  "all",
  ret = c(
    "threshold",
    "sensitivity",
    "specificity",
    "tp",
    "tn",
    "fp",
    "fn",
    "npv",
    "ppv",
    "tnr",
    "fnr"
  )
))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
```

##### (NGT + AGT) vs. CFRD

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = black_agt_cfrd)
roc_plot(r)
gt(data.frame(coords(r, "best"))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
gt(data.frame(coords(
  r,
  "all",
  ret = c(
    "threshold",
    "sensitivity",
    "specificity",
    "tp",
    "tn",
    "fp",
    "fn",
    "npv",
    "ppv",
    "tnr",
    "fnr"
  )
))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
```

@@

```{r}
more_ngt_agt <- ngt_agt |> filter(Race == "More than one race")
more_agt_cfrd <- agt_cfrd |> filter(Race == "More than one race")
```

##### NGT vs. (AGT + CFRD)

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = more_ngt_agt)
roc_plot(r)
gt(data.frame(coords(r, "best"))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
gt(data.frame(coords(
  r,
  "all",
  ret = c(
    "threshold",
    "sensitivity",
    "specificity",
    "tp",
    "tn",
    "fp",
    "fn",
    "npv",
    "ppv",
    "tnr",
    "fnr"
  )
))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
```

##### (NGT + AGT) vs. CFRD

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = more_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
gt(data.frame(coords(
  r,
  "all",
  ret = c(
    "threshold",
    "sensitivity",
    "specificity",
    "tp",
    "tn",
    "fp",
    "fn",
    "npv",
    "ppv",
    "tnr",
    "fnr"
  )
))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
```

@@

```{r}
other_ngt_agt <- ngt_agt |> filter(Race == "Other race")
other_agt_cfrd <- agt_cfrd |> filter(Race == "Other race")
```

##### NGT vs. (AGT + CFRD)

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = other_ngt_agt)
roc_plot(r)
gt(data.frame(coords(r, "best"))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
gt(data.frame(coords(
  r,
  "all",
  ret = c(
    "threshold",
    "sensitivity",
    "specificity",
    "tp",
    "tn",
    "fp",
    "fn",
    "npv",
    "ppv",
    "tnr",
    "fnr"
  )
))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
```

##### (NGT + AGT) vs. CFRD

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = other_agt_cfrd)
roc_plot(r)
gt(data.frame(coords(r, "best"))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
gt(data.frame(coords(
  r,
  "all",
  ret = c(
    "threshold",
    "sensitivity",
    "specificity",
    "tp",
    "tn",
    "fp",
    "fn",
    "npv",
    "ppv",
    "tnr",
    "fnr"
  )
))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
```

@@

```{r}
hispanic_ngt_agt <- ngt_agt |> filter(Hispanicrace == "Yes")
hispanic_agt_cfrd <- agt_cfrd |> filter(Hispanicrace == "No")
```

##### NGT vs. (AGT + CFRD)

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = hispanic_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
gt(data.frame(coords(
  r,
  "all",
  ret = c(
    "threshold",
    "sensitivity",
    "specificity",
    "tp",
    "tn",
    "fp",
    "fn",
    "npv",
    "ppv",
    "tnr",
    "fnr"
  )
))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
```

##### (NGT + AGT) vs. CFRD

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = hispanic_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
gt(data.frame(coords(
  r,
  "all",
  ret = c(
    "threshold",
    "sensitivity",
    "specificity",
    "tp",
    "tn",
    "fp",
    "fn",
    "npv",
    "ppv",
    "tnr",
    "fnr"
  )
))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
```

@@

```{r}
non_hispanic_ngt_agt <-
  ngt_agt |> filter(Race == "Black or African American")
non_hispanic_agt_cfrd <-
  agt_cfrd |> filter(Race == "Black or African American")
```

##### NGT vs. (AGT + CFRD)

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = roc_df)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
gt(data.frame(coords(
  r,
  "all",
  ret = c(
    "threshold",
    "sensitivity",
    "specificity",
    "tp",
    "tn",
    "fp",
    "fn",
    "npv",
    "ppv",
    "tnr",
    "fnr"
  )
))) |>
  fmt_number(decimals = 3, drop_trailing_zeros = T)
```
